Development of User-Friendly\\System Identification Techniques

### 2016-03-03 ch02-qlogms/excitation-design.tex
Guidelines improved

  Consequently, the complete multisine has a period $T_{u(t)}$ that is the (least) common multiple of the period of its components:
  \begin{equation}
    T_{u(t)}  = \lcm \set{T_1, \ldots, T_F}
      = \lcm \set{f_1^{-1}, \ldots, f_F^{-1}}
    \text{.}
  \end{equation}

@@

  \begin{figure}[ht]
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.5\figurewidth}
    \input{\thisDir/figs/freqGrid.tikz}
    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
    \TODO{use same color conventions here}
    \label{fig:excitation:freqGrids}
  \end{figure}

@@

@@

  At the higher frequency bands, an approximately constant quality is still obtained for the (compensated) quasi-logarithmic signals.
  At lower frequencies, however, the logarithmically spaced signals perform only slightly better than the linearly spaced excitation signal.
  This is due to the fact that as the damping $\damping$ decreases, the $3\unit{dB}$ bandwidth of the resonance decreases and therefore less points can be fitted in this bandwidth at the lower frequencies.
  In our case, only $1$ line was excited in the $3 \unit{dB}$ bandwidth (respectively $0.4 \unit{Hz}$ and $0.8\unit{Hz}$ wide) of the systems with the lowest resonance frequencies.
  It is clearly unfeasible to estimate the five parameters in
  \eqref{eq:excitation:secondOrderSystemDTidentifiable} using this little information in the $3\unit{dB}$ bandwidth of the system.
  In other words, the resonances of the systems at low frequencies, can no longer be considered to lie within the bulk of the logarithmic part of the quasi-logarithmic frequency grids.
  This can also be understood from equation \eqref{eq:excitation:systemInBulk:generic}.
  In that equation, $\alpha = \alpha^{\star} = 1 + \damping$ such that
  \begin{equation}
    2 \pi \Delta f \leq (\damping - \damping^2) \wn
    \label{eq:excitation:systemInBulk:tuned}
  \end{equation}
  is the necessary condition for the system bandwidth to lie within the bulk of the frequency grid when the frequency spacing has been tuned according to \secref{sec:excitation:optimAlpha}.
  For this simulation, with $\Delta f=1\unit{Hz}$, $\damping=0.05$, this evaluates to $\wn \geq 132 \unit{rad/s} = 21 \unit{Hz}$.
  The system with $\wR = 20 \unit{Hz} < 21 \unit{Hz}$ is still well-identified, even though `only' $3$ lines are excited in its bandwidth.
  In that particular case, the frequency grid and the resonance peak are well-aligned ($\beta \approx 0$), which leads to a reduced variance (see also \figref{fig:excitation:worstCaseBeta}).

  We do see, however, that the variance in the vicinity of the resonance of every system is lower than in the case of a linearly spaced excitation

@@

\TODO{vuistregels herhalen in kader: $\alpha \sim \damping[\min]$, $\wn[\min] \sim \Delta \omega, \damping[\min]$}
\TODO{evt. plot vuistregels voor freq.grid.}

>>>>

  Consequently, the complete multisine has a period $T_{u(t)}$ that is the (least) common multiple of the period of its components:
  \begin{equation}
    T_{u(t)}  = \lcm \set{T_1, \ldots, T_F}
      = \lcm \set{f_1^{-1}, \ldots, f_F^{-1}}
  \end{equation}
  if a common multiple exists, i.e. $T_{u(t)} = n_1 T_1 = \ldots = n_F T_F$ with $n_i \in \NaturalNumbersWithoutZero$ for $i \in \set{1,\ldots,F}$.

@@

  \begin{figure}[ht]
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.5\figurewidth}
    \input{\thisDir/figs/freqGrid.tikz}
    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
    \label{fig:excitation:freqGrids}
  \end{figure}

@@

   \begin{guideline}[Design the logarithmic grid for the damping of the system: $\alpha \leq  1 + \xi_{\min}$]
   To measure a resonant system with damping $\damping > \damping[\min]$ well, a (pink) quasi-logarithmic multisine with frequency ratio $\frac{\omega_k}{\omega_{k-1}} \leq \alpha \leq 1 + \damping[\min]$ is recommended.
   Smaller frequency ratios provide more measurement points at the cost of a reduced \gls{SNR} per frequency bin.
   As such, $\alpha = 1 + \damping \isdef \alpha^{\star}$ provides the required resolution and the best \gls{SNR} per bin.
\end{guideline}

@@

  At the higher frequency bands, an approximately constant quality is still obtained for the (compensated) quasi-logarithmic signals.
  At lower frequencies, however, the logarithmically spaced signals perform only slightly better than the linearly spaced excitation signal.
  This is due to the fact that as the damping $\damping$ decreases, the $3\unit{dB}$ bandwidth of the resonance decreases and therefore less points can be fitted in this bandwidth at the lower frequencies.
  In our case, only $1$ line was excited in the $3 \unit{dB}$ bandwidth (respectively $0.4 \unit{Hz}$ and $0.8\unit{Hz}$ wide) of the systems with the lowest resonance frequencies.
  It is clearly unfeasible to estimate the five parameters in
  \eqref{eq:excitation:secondOrderSystemDTidentifiable} using this little information in the $3\unit{dB}$ bandwidth of the system.
  In other words, the resonances of the systems at low frequencies, can no longer be considered to lie within the bulk of the logarithmic part of the quasi-logarithmic frequency grids.
  This can also be understood from equation \eqref{eq:excitation:systemInBulk:generic}.
  In that equation, $\alpha = \alpha^{\star} = 1 + \damping$ (see \secref{sec:excitation:optimAlpha}) such that the following guideline is the necessary condition for the $3\unit{dB}$ bandwidth of the system to lie within the bulk of the frequency grid.

\begin{guideline}[Choose $2 \pi \Delta f \leq (\damping - \damping^2) \wn$]
\label{guide:excitation:systemInBulk:tuned}
 A quasi-logarithmic multisine with frequency resolution $\Delta f$ and tuned frequency spacing $\alpha=1+\damping$ is only guaranteed to properly excite resonances peaks with damping $\damping$ and resonance frequency $\wn$ when 
  \begin{equation}
    2 \pi \Delta f \leq (\damping - \damping^2) \wn 
    \approx \damping \wn \text{ if $\damping \ll 1$}
    \text{.}
    \label{eq:excitation:systemInBulk:tuned}
  \end{equation}
  \end{guideline}

  \begin{remark}
  \guideref{guide:excitation:systemInBulk:tuned} can be interpreted either as
  \begin{itemize}
     \item  a lower limit on the allowable $\wn$ of the system (when the multisine has been designed ($\Delta f$ and $\damping$ are fixed)), or 
     \item as a requirement on the measurement time $\Tm = (\Delta f)^{-1}$ when lower bounds on $\damping$ and $\wn$ are known.
   \end{itemize}
  \end{remark}

  For this simulation, with $\Delta f=1\unit{Hz}$, $\damping=0.05$, \eqref{eq:excitation:systemInBulk:tuned} evaluates to $\wn \geq 132 \unit{rad/s} = 21 \unit{Hz}$.
  The system with $\wR = 20 \unit{Hz} < 21 \unit{Hz}$ is still well-identified, even though `only' $3$ lines are excited in its bandwidth.
  In that particular case, the frequency grid and the resonance peak are well-aligned ($\beta \approx 0$), which leads to a reduced variance (see also \figref{fig:excitation:worstCaseBeta}).

  We do see, however, that the variance in the vicinity of the resonance of every system is lower than in the case of a linearly spaced excitation.

@@

### 2016-03-03 front-and-back-matter/frontmatter.tex
Update title page + summary
List of Guidelines
Guidelines improved

\input{front-and-back-matter/summary.inc.tex}
\input{front-and-back-matter/acknowledgements.inc.tex}

@@

\listoffigures
\listoftables
% \TOCInsert{section}{List of Listings}   \lstlistoflistings %TODO: fix this

\printglossary[type=\acronymtype,style=long,toctitle={List of Acronyms}, title={List of Acronyms}] %TODO: change format, set order, change title to "List of Abbreviations"
\glsaddall[types=symbols]
\printglossary[type=symbols,style=altlong4col,title={List of Symbols},toctitle={List of Symbols}]

>>>>

\input{front-and-back-matter/acknowledgements.inc.tex}

@@

\listoffigures
\listoftables

%http://tex.stackexchange.com/questions/74857/toc-like-list-of-definitions-using-theorem-environments
\renewcommand{\listtheoremname}{List of Guidelines}
\listoftheorems[ignoreall,show=guideline]

% \TOCInsert{section}{List of Listings}   \lstlistoflistings %TODO: fix this

\printglossary[type=\acronymtype,style=long,toctitle={List of Abbreviations}, title={List of Abbreviations}] %TODO: change format

\glsaddall[types=symbols]
\printglossary[type=symbols,style=altlong4col,title={List of Symbols},toctitle={List of Symbols}]
